The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-18 repeater-vladata.tex
fixing axis label on spectra

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a find grid of DM ($\Delta DM=1 \rm{pc} \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

@@

There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign. We modeled the event detection probability as a Poisson probability with a rate parameter that evolves linearly with time relative to first burst detection, $\lambda = a + b * (\rm{MJD}_i - 57623)$. By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence. This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.

>>>>

\subsubsection{Spectra}
\label{sec:spec}
Figure \ref{fig:sgram} shows the dynamic spectra of all nine bursts detected by the VLA. We improved on the initial analysis presented in \citet{LOC} by using a better calibration scheme and optimizing the detection significance over a fine grid of DM ($\Delta \rm{DM}=1 \rm{pc} \rm{cm}^{-3}$). Table \ref{tab:spec} shows the improved burst parameters using this new scheme.

@@

There is weak evidence that the \frb\ burst rate changed during the last 27 hours of the S-band campaign. We modeled the event detection probability as a Poisson probability function, $P_i(\lambda)$, with rate parameter that evolves linearly in time relative to the first VLA burst $\lambda = a + b (\rm{MJD}_i - 57623)$. By directly sampling the joint probability distribution, $\prod_{i} P_i$, we can exclude a constant rate with $\sim$85\% confidence. This weak constraint is consistent with the broader trend seen by the VLA and Arecibo.
